The Folly of Passwords

### 2014-12-09 paper.tex
Written more and added base Vagrantfile.

In this paper, we will explore the feasibiity of adopting some of
these authentication methods within an enterprise. The primary consideration
is around detailing the setup and maintenance steps and whether any
method can be justifiably ruled out in the early phases of a feasibility
study. In section~\ref{sec:evaluation}, we will look at how the evaluation
was carried out and the remaining sections detail that evaluation against each
considered method.

@@

TIQR was ruled out as the aims of the project to date seem to be based around
web-based logins only, which does not fit our defined enterprise need of
supporting desktop computer login.

>>>>

In this chapter, we will explore the feasibiity of adopting some of
these authentication methods within an enterprise. The primary consideration
is around detailing the setup and maintenance steps and whether any
method can be justifiably ruled out in the early phases of a feasibility
study. In section~\ref{sec:evaluation}, we will look at how the evaluation
was carried out and the remaining sections detail that evaluation against each
considered method.

@@

TIQR was ruled out as the aims of the project to date seem to be based around
web-based logins only, which does not fit our defined enterprise need of
supporting desktop computer login. Challenge/response tokens are also
out of scope for this paper as they do not differ too greatly from OTP
token and our focus is primarily on evaluating a small, but diverse, set
of password alternatives.
